INSTRUCTIONS TO PREPARE A FULL PAPER FOR THE 9th EUROPEAN CONGRESS ON COMPUTATIONAL METHODS IN APPLIED SCIENCES AND ENGINEERING\break ECCOMAS CONGRESS 2024

### 2024-03-12 paper/paper.tex
update all figures and paper

\subsubsection{Singular values of POD modes}

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_loc_svals_left.pdf}
  \caption{A really Awesome Image}\label{fig:loc_svals_left}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_loc_svals_inner.pdf}
  \caption{A really Awesome Image}\label{fig:loc_svals_inner}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{../figures/beam/fig_loc_svals_right.pdf}
  \caption{A really Awesome Image}\label{fig:loc_svals_right}
\endminipage
\end{figure}

\subsubsection{Projection Error}
The projection error is computed for a test set for each configuration that was computed
using the FOM. Each test set has size $n_{test}$.

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_proj_error_left.pdf}
  \caption{A really Awesome Image}\label{fig:proj_error_left}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_proj_error_inner.pdf}
  \caption{A really Awesome Image}\label{fig:proj_error_inner}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{../figures/beam/fig_proj_error_right.pdf}
  \caption{A really Awesome Image}\label{fig:proj_error_right}
\endminipage
\end{figure}

>>>>

\subsubsection{Distributed approximate POD}

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_loc_svals_left.pdf}
  \caption{Singular valus left}\label{fig:loc_svals_left}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_loc_svals_inner.pdf}
  \caption{Singular valus inner}\label{fig:loc_svals_inner}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{../figures/beam/fig_loc_svals_right.pdf}
  \caption{Singular valus right}\label{fig:loc_svals_right}
\endminipage
\end{figure}

% \subsubsection{Projection Error}
% The projection error is computed for a test set for each configuration that was computed
% using the FOM. Each test set has size $n_{test}$.

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_proj_error_left_hapod.pdf}
  \caption{Projection error hapod}\label{fig:proj_error_left_hapod}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_proj_error_inner_hapod.pdf}
  \caption{Projection error hapod}\label{fig:proj_error_inner_hapod}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{../figures/beam/fig_proj_error_right_hapod.pdf}
  \caption{Projection error hapod}\label{fig:proj_error_right_hapod}
\endminipage
\end{figure}

\subsubsection{Heuristic range finder}

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_proj_error_left_heuristic.pdf}
  \caption{Projection error }\label{fig:proj_error_left_heuristic}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_proj_error_inner_heuristic.pdf}
  \caption{Projection error }\label{fig:proj_error_inner_heuristic}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{../figures/beam/fig_proj_error_right_heuristic.pdf}
  \caption{Projection error }\label{fig:proj_error_right_heuristic}
\endminipage
\end{figure}
